Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2020-08-07 FDT2020/Introduction.tex
Edits in the experimental section through the TAP part. Fixing accents in JaJa's name.
Moved the Carr-Vempala figure to the experimental section, typo fixes, questions

In the \textsc{minimum vertex cover problem (VC)} we are given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$. A subset of $U$ of $V$ is a \textit{vertex cover} if for all $e\in E$ at least one endpoint of $e$ is in $U$. The goal in VC is to find the minimum-cost vertex cover. The linear programming relaxation for VC is
\begin{equation}
\min \{cx \; : \; x_u + x_v \geq	 1 \text{ for all } e=uv \in E, \; x\in [0,1]^{V}\}.
\end{equation}
The integrality gap of this formulation is exactly 2 \cite{davids}. Austrin, Khot and Safra~\cite{UGhardVC} show that it is UG-hard to approximate VC within any factor strictly better than 2. We compare  FDT and the feasbility pump heuristic \cite{fp1} on the small instances of the PACE\footnote{ Parameterized Algorithms and Computational Experiments: \url{https://pacechallenge.org/2019/}} 2019 challenge test cases \cite{PACE}. FDT was 3-5x slower, but still ran in seconds. It always gave a better vertex cover. For some instances the FDT solution's relative gap with respect to the optimal was half that of feasibility pump.
\subsubsection{Tree augmentation problem}
In the \textsc{Tree Augmentation Problem (TAP)} we are given a  graph $G=(V,E)$, a spanning tree $T$ of $G$ and a cost vector $c\in \mathbb{R}^{E\setminus T}_{\geq 0}$. A subset $F$ of $E\setminus T$ is called a \textit{feasible augmentation} if $(V,T\cup F)$ is a 2-edge-connected graph. In TAP we seek the minimum cost feasible augmentation. The natural linear programming relaxation for TAP is 
\begin{equation}
\min \{cx\; : \; \sum_{\ell \in \cov(e)} x_{\ell} \geq 1 \text{ for } e\in T, \; x\in [0,1]^{E\setminus T}\}.
\end{equation}
where $\cov(e)$ for $e \in T$ is the set of edges $\ell \in E\setminus T$ such that $e$ is in the unique cycle of $T\cup \{\ell\}$. Another way to think of $\cov(e)$ is that if we remove edge $e$ from tree $T$, this partitions the vertices into two connected sets $U$ and $V-U$.  Then $\cov(e) = \delta(U)$ is the set of edges $\ell \neq e$ that cross the cut between $U$ and $V-U$, and whose addition would reconnect the tree. We call the LP above the cut LP. The integrality gap of the cut LP is known to be between $\frac{3}{2}$ \cite{32gaptap} and $2$ \cite{FJ81}. We create random fractional extreme points of the cut LP and apply FDT to find integral solutions. For our instances, the ratio of the value of the feasible solution to the LP lower bound is always below $\frac{3}{2}$. This provides evidence that the integrality gap for such instances may be less than $\frac{3}{2}$.

@@

There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP, see \cite{tspbook}) or 2EC 
%\cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
Benoit and Boyd~\cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices. Alexander et al. \cite{alexander2006integrality} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $g(\2ec)$ on graphs with at most 10 vertices.

Consider a graph $G=(V,E)$. A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$ (see Figure \ref{fig:CVpoint})
%\cindy{Every pair of vertices on the cycle is connected this way? It sounds like that, though I don't recall that being necessary. We probably have a figure from an old version we could include if it's not too much trouble.  This will help reviewers and future readers understand much more easily, especially that there could be far more than 12 vertices in the overall solution.}

\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?} \cindy{Yes that would be fine, if the reader could also use that figure then.  They could page forward to see the figure when reading the introduction.}

\begin{figure}
\centering
\begin{tikzpicture}[scale=0.4]

\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (0,-4)};
\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(2.83,2.83) (-4,0)};
\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (-2.83,-2.83)};
\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-2.83,2.83) (2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (2.83,2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (-2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (-2.83,2.83)};

\draw[black,fill=white] (0,4) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (4,0) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (0,-4) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (-4,0) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (-2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (-2.83,2.83) ellipse (0.5 cm  and 0.5 cm);

\node (1) at (0,4) {{1}};
\node (2) at (2.83,2.83) {{2}};
\node (3) at (4,0) {{3}};
\node (4) at (2.83,-2.83) {{4}};
\node (5) at (0,-4) {{5}};
\node (6) at (-2.83,-2.83) {{6}};
\node (7) at (-4,0) {{7}};
\node (8) at (-2.83,2.83) {{8}};
\end{tikzpicture}
\caption{A Carr-Vempala point with 8 vertices on its cycle. Solid lines are edges with value strictly between $0$ and $1$. Dashed edges represent paths where each edge on the path has $x_e =1$. There can be an arbitrary number of degree-$2$ vertices on the dashed paths.}
\label{fig:CVpoint}
\end{figure}

>>>>

In the \textsc{minimum vertex cover problem (VC)} we are given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$. A subset of $U$ of $V$ is a \textit{vertex cover} if for all $e\in E$ at least one endpoint of $e$ is in $U$. The goal in VC is to find the minimum-cost vertex cover. The linear programming relaxation for VC is
\begin{equation}
\min \{cx \; : \; x_u + x_v \geq	 1 \text{ for all } e=uv \in E, \; x\in [0,1]^{V}\}.
\end{equation}
The integrality gap of this formulation is exactly 2 \cite{davids}. Austrin, Khot and Safra~\cite{UGhardVC} show that it is UG-hard to approximate VC within any factor strictly better than 2. We compare  FDT and the feasbility pump heuristic \cite{fp1} on the small instances of the PACE\footnote{ Parameterized Algorithms and Computational Experiments: \url{https://pacechallenge.org/2019/}} 2019 challenge test cases \cite{PACE}. FDT was 3-5x slower, but still ran in seconds. It always gave a better vertex cover. For some instances the FDT solution's relative gap with respect to the optimal was half that of feasibility pump.
\subsubsection{Tree augmentation problem}
In the \textsc{Tree Augmentation Problem (TAP)} we are given a  graph $G=(V,E)$, a spanning tree $T$ of $G$ and a cost vector $c\in \mathbb{R}^{E\setminus T}_{\geq 0}$. A subset $F$ of $E\setminus T$ is called a \textit{feasible augmentation} if $(V,T\cup F)$ is a 2-edge-connected graph. In TAP we seek the minimum cost feasible augmentation. The natural linear programming relaxation for TAP is 
\begin{equation}\label{eq:cutLP}
\min \{cx\; : \; \sum_{\ell \in \cov(e)} x_{\ell} \geq 1 \text{ for } e\in T, \; x\in [0,1]^{E\setminus T}\}.
\end{equation}
where $\cov(e)$ for $e \in T$ is the set of edges $\ell \in E\setminus T$ such that $e$ is in the unique cycle of $T\cup \{\ell\}$. Another way to think of $\cov(e)$ is that if we remove edge $e$ from tree $T$, this partitions the vertices into two connected sets $U$ and $V-U$.  Then $\cov(e) = \delta(U)$ is the set of edges $\ell \neq e$ that cross the cut between $U$ and $V-U$, and whose addition would reconnect the tree. We call the LP above the cut LP. The integrality gap of the cut LP is known to be between $\frac{3}{2}$ \cite{32gaptap} and $2$ \cite{FJ81}. We create random fractional extreme points of the cut LP and apply FDT to find integral solutions. For our instances, the ratio of the value of the feasible solution to the LP lower bound is always below $\frac{3}{2}$. This provides evidence that the integrality gap for such instances may be less than $\frac{3}{2}$.

@@

There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP, see \cite{tspbook}) or 2EC.
%\cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
Benoit and Boyd~\cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices. Alexander et al. \cite{alexander2006integrality} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $g(\2ec)$ on graphs with at most 10 vertices.

Consider a graph $G=(V,E)$. A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$ (see Figure \ref{fig:CVpoint}).
%\cindy{Every pair of vertices on the cycle is connected this way? It sounds like that, though I don't recall that being necessary. We probably have a figure from an old version we could include if it's not too much trouble.  This will help reviewers and future readers understand much more easily, especially that there could be far more than 12 vertices in the overall solution.}

%\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?} \cindy{Yes that would be fine, if the reader could also use that figure then.  They could page forward to see the figure when reading the introduction.}

### 2020-08-07 FDT2020/main-section.tex
Moved the Carr-Vempala figure to the experimental section, typo fixes, questions

We first describe the polyhedral version of Christofides' algorithm specifically for Carr-Vempala points.
\cindy{I think it would be very helpful for the reader for you to remind them of the classic (graph-based, not polyhedral) metric (triangle-inequality) Christofides algorithm here and argue that it applies to 2EC.  Most people will remember Christofides' TSP approximation algorithm because it's so classic.  But it's easy to remind people.  Then it would be helpful to explain that when you give the LP in (\ref{ojoinaverage}) how that relates to Christofides.  If this paper is accepted, all kinds of CS/OR researchers may want to read it, so we should make their job as easy as possible.  It would be nice for others to use FDT and to build off it.}
Let $x$ be a Carr-Vempala point defined on a graph $G=(V,E)$. It is well known that $\frac{|V|-1}{|V|}\cdot x$ is in the convex hull of incidence vectors of spanning trees of $G$.
\cindy{The statement before this depends very much on the audience.  For those who study polyhedral combinatorics especially for TSP and who know what a Carr-Vempala point is off the top of their heads, it may be well known.  For people who generally do combinatorial optimization, I would not expect them to know this. So this kind of phrasing might annoy a reader.  General rule: either a statement is really obvious (so just state it), or it is not (so give a reference or justification). Otherwise (and I know you don't intend this), you are implying the reader is stupid if they don't see the argument right away. Of course, it's the authors' job to teach and convince the reader. Thus one should avoid phrases like ``It's obvious/trivial that...'' and similar phrases. I would change the sentence before this comment to ``The vector $\frac{|V|-1}{|V|}\cdot x$ is in the convex hull...'' and give a short justification or reference. Or ``Foo and Barr (cite Foo and Bar's paper) argue that ... is in the convex hull...'' I'm sure I could figure this out if a had a little time to think, but I don't have that time now.}
Hence, we can write $\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G$, $\chi^{T_i}$ is its incidence vector, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$. Let $O_i$ be the set of odd-degree vertices of $T_i$. It is easy to see that $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, namely $O_i\join(G)$~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.}.
\cindy{Here is another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.'' Also, do you mean that $x/2$ is in the convex hull of the incident vectors of all $O_i$-joins for any spanning tree $T_i$?  If so, it would be good to make that clear.  Since I will not make it through every word of Sections 2-4 if you submit today, I recommend looking for similar places in those sections.}

\cindy{Do you have to precompute the joins?  Does that mean generating spanning trees before setting up the LP?  Or generating them on the fly?  Only minimum-weight spanning trees?  I haven't had a lot of time to think about this.}
 We solve the following LP that allows us to find parity corrections that are good for the whole convex combination.
\begin{equation}\label{ojoinaverage}
\min \{ \alpha:\;\sum_{i=1}^{k} \lambda_i y^i = \alpha \cdot x,\;  y^i \in O_i\join(G) \; \mbox{for $i\in [k]$}\}.
\end{equation}
The variables in the above LP are $y^i\in \mathbb{R}^{E_x}_{
\geq 0}$ for $i\in [k]$. For each $i\in [k]$ we have $y^i\in O_i\join(G_x)$. This formulation allows the instance specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$. Recall that a Carr-Vempala point consists of a signle cycle of fractional edges.  Figure \ref{fdtvschris} shows FDT's solutions on all Carr-Vempala points that have 10 vertices on the cycle formed by fractional edges. We show for these points the apporoximation factor provided by FDT is always better than those from the polyhedral version of Christofides' algorithm. In more details, in Figure \ref{fdtvschris} the horizontal axis of the plot is indexed with the 60 Carr-Vempala points that we considered. For each Carr-Vempala point $x$, there are two data points. The value of the first data point depicted by a circle on the vertical axis is $\frac{|V|-1}{|V|}+\alpha$  and $\alpha$ is the optimal solution to (\ref{ojoinaverage}). 
The value of the second data point depicted by a cross on the vertical axis is $C$ where $C$ is obtained from applying Theorem \ref{FDT2EC} to $x$. In other words, Figure \ref{fdtvschris} is comparing the instance-specific upper bound on integrality gap certified by Christofides' algorithm to the approximation factor of the FDT algorithm for 2EC.

>>>>

We first describe the polyhedral version of Christofides' algorithm specifically for Carr-Vempala points.
\cindy{I think it would be very helpful for the reader for you to remind them of the classic (graph-based, not polyhedral) metric (triangle-inequality) Christofides algorithm here and argue that it applies to 2EC.  Most people will remember Christofides' TSP approximation algorithm because it's so classic.  But it's easy to remind people.  Then it would be helpful to explain that when you give the LP in (\ref{ojoinaverage}) how that relates to Christofides.  If this paper is accepted, all kinds of CS/OR researchers may want to read it, so we should make their job as easy as possible.  It would be nice for others to use FDT and to build off it.}
Let $x$ be a Carr-Vempala point defined on a graph $G=(V,E)$. It is well known that $\frac{|V|-1}{|V|}\cdot x$ is in the convex hull of incidence vectors of spanning trees of $G$.
\cindy{Is this for any feasible solution, or extreme point of the subtour LP or just Carr-Vempala points?  It seems that it's for any feasible point since you don't remind the reader about Carr-Vempala points until later.}
\cindy{The statement before this depends very much on the audience.  For those who study polyhedral combinatorics especially for TSP and who know what a Carr-Vempala point is off the top of their heads, it may be well known.  For people who generally do combinatorial optimization, I would not expect them to know this. So this kind of phrasing might annoy a reader.  General rule: either a statement is really obvious (so just state it), or it is not (so give a reference or justification). Otherwise (and I know you don't intend this), you are implying the reader is stupid if they don't see the argument right away. Of course, it's the authors' job to teach and convince the reader. Thus one should avoid phrases like ``It's obvious/trivial that...'' and similar phrases. I would change the sentence before this comment to ``The vector $\frac{|V|-1}{|V|}\cdot x$ is in the convex hull...'' and give a short justification or reference. Or ``Foo and Barr (cite Foo and Bar's paper) argue that ... is in the convex hull...'' I'm sure I could figure this out if a had a little time to think, but I don't have that time now.}
\cindy{I'm going to remove things like ``It's easy to see that,'' where I can. But we may need to add a justification or reference.}
Hence, we can write $\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G$, $\chi^{T_i}$ is its incidence vector, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$. Let $O_i$ be the set of odd-degree vertices of $T_i$. We have $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, denoted $O_i\join(G)$~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.}.
\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}

\cindy{Do you have to precompute the joins (If they are more than the spanning trees themselves)?  Does that mean generating spanning trees before setting up the LP?  Or generating them on the fly?  Only minimum-weight spanning trees?  It seems that with a little more explanation, a reader who has not been immersed in 2EC and TSP could follow this.}

 We solve the following LP that allows us to find parity corrections that are good for the whole convex combination.
\begin{equation}\label{ojoinaverage}
\min \{ \alpha:\;\sum_{i=1}^{k} \lambda_i y^i = \alpha \cdot x,\;  y^i \in O_i\join(G) \; \mbox{for $i\in [k]$}\}.
\end{equation}
The variables in the above LP are $y^i\in \mathbb{R}^{E_x}_{
\geq 0}$ for $i\in [k]$. For each $i\in [k]$ we have $y^i\in O_i\join(G_x)$.
\cindy{You say the $y^i$ are LP variables, not integers. It even looks like they can even be more than $1$. What does it mean for a non-binary vector to be in a set of binary variables?  I would have expected the lambdas to be the variables, given their use as the convex combination multipliers in most of the paper.}
This formulation allows the instance-specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$. Recall that a Carr-Vempala point consists of a single cycle of fractional edges.  Figure \ref{fdtvschris} shows FDT's solutions on all Carr-Vempala points that have 10 vertices on the cycle formed by fractional edges. We show for these points the apporoximation factor provided by FDT is always better than those from the polyhedral version of Christofides' algorithm. In Figure \ref{fdtvschris} the horizontal axis of the plot is indexed with the 60 Carr-Vempala points that we considered. For each Carr-Vempala point $x$, there are two data points. The value of the first data point depicted by a circle on the vertical axis is $\frac{|V|-1}{|V|}+\alpha$  and $\alpha$ is the optimal solution to (\ref{ojoinaverage}). \cindy{TODO: say when giving the LP~(\ref{ojoinaverage}) how that gives a solution to TAP with this value.}
The value of the second data point depicted by a cross on the vertical axis is $C$ where $C$ is obtained from applying Theorem \ref{FDT2EC} to $x$. In other words, Figure \ref{fdtvschris} is comparing the instance-specific upper bound on integrality gap certified by Christofides' algorithm to the approximation factor of the FDT algorithm for 2EC.

\begin{figure}
\centering
\begin{tikzpicture}[scale=0.4]

\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (0,-4)};
\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(2.83,2.83) (-4,0)};
\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (-2.83,-2.83)};
\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-2.83,2.83) (2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (2.83,2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (-2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (-2.83,2.83)};

\draw[black,fill=white] (0,4) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (4,0) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (0,-4) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (-4,0) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (-2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (-2.83,2.83) ellipse (0.5 cm  and 0.5 cm);

\node (1) at (0,4) {{1}};
\node (2) at (2.83,2.83) {{2}};
\node (3) at (4,0) {{3}};
\node (4) at (2.83,-2.83) {{4}};
\node (5) at (0,-4) {{5}};
\node (6) at (-2.83,-2.83) {{6}};
\node (7) at (-4,0) {{7}};
\node (8) at (-2.83,2.83) {{8}};
\end{tikzpicture}
\caption{A Carr-Vempala point with 8 vertices on its cycle. Solid lines are edges with value strictly between $0$ and $1$. Dashed edges represent paths where each edge on the path has $x_e =1$. There can be an arbitrary number of degree-$2$ vertices on the dashed paths.}
\label{fig:CVpoint}
\end{figure}
